Offline Reinforcement Learning with In-Sample Tsallis Regularized Policy

### 2023-04-22 paper/main.tex
added more details

We can write out the regularized policy for general Tsallis entropy regularization for any $q$\footnotemark\footnotetext{Different to prior works \cite{Lee2018-TsallisRAL,Nachum18a-tsallis}, our definition of $\psi$ has an additional $\frac{1}{q-1}$ term in order to be accommodated in the $q$-exponential function, see Appendix \ref{apdx:derivation} for derivation.}:
\begin{align}
    \pi(a|s) = \exp_q \AdaBracket{\frac{Q(s,a)}{\tau } - {\psi}\AdaBracket{\frac{Q(s, \cdot)}{\tau }}}, \,\,
    {\psi}\AdaBracket{\frac{Q(s,\cdot)}{\tau}} \doteq \frac{\sum_{a\in K(s)} \frac{Q(s,a)}{\tau} - 1 }{|K{(s)}|} + \frac{1}{q-1}.
    \label{eq:tsallis_policy}
\end{align}
  $K(s)$ is the set of highest-value actions satisfying $1 \!+\! i\frac{Q(s,a_{(i)})}{\tau} \!>\! \sum_{j=1}^{i}\frac{Q(s,a_{(j)})}{\tau}$, with $a_{(j)}$ denotes the $j$-th largest action.
  Intuitively, the policy first sorts actions by $a_{(1)}, \dots, a_{(|\mathcal{A}|)}$ and then compute the threshold $\psi$.
  Suppose $Q(s, a_{(j+1)}) \leq \psi \leq Q(s, a_{(j)})$, then all actions from $j+1$ are truncated and have zero probability of being selected.
  The truncation effect can be controlled by $\tau$.

@@

It is worth noting that unlike for online RL, where the OOD actions can lead to sampling more around the low sample region and eventually correction of the values, in offline RL this is impossible.
Instead, many of the existing works propose to force the learned policy to be close to the behavior policy \cite{Dadashi2021-pseudoMetricOffline,Fujimoto2019-InSampleMax,Fujimoto2021-minimalist,Nair2021-awac}.
This is often achieved by adding a regularizer penalizing deviating from the behavior policy \cite{Ghasemipour2021-EMaQ,Kumar2019-BootstrapErrorQlearningMMD,Jaques2020-OfflineDialog,Wu2020-BehaviorRegularizedAC}, e.g. incorporating the KL penalty $\tau\KLany{\pi(\cdot|s)}{\datasetPolicy(\cdot|s)}$ leads to the policy form $\pi(a|s)\propto\datasetPolicy(a|s)\exp\AdaBracket{\tau^{-1}Q_{\pi}(s,a)}$ where the learned policy must have the same support of the behavior policy.
This idea is shared by the \emph{in-sample} methods that enforce the support of the learned policy to be within the behavior policy $\pi \preceq \datasetPolicy$ \cite{Fujimoto2019-InSampleMax,Kostrikov2022-implicitQlearning,Xiao2023-InSampleSoftmax}, which is achieved by only updating for the actions in the dataset.

@@

To alleviate the OOD error, \citet{Fujimoto2019-InSampleMax} proposed the in-sample Bellman optimality equation to update only for actions present in the dataset:
\begin{align}
    \datasetOptimalQ(s,a) = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{\max_{a': \datasetPolicy(a'|s') > 0} \datasetOptimalQ(s',a')}.
    \label{eq:hardmax_offline}
\end{align}
Later, \citet{Xiao2023-InSampleSoftmax} proposed in-sample softmax to better estimate the policy inside the bracket since in the continuous case the hard max operator might be difficult to solve for.
By regularizing with the Shannon entropy $\tau \entropy$ and imposing the dataset support constraint, the in-sample softmax Bellman optimality equation has the following evaluation step:
% \begin{align}
%     \datasetOptimalQ(s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a': \datasetPolicy(a'|s') > 0} \!\!\!\!\! \pi(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau\entropy(\cdot|s')}}.
%     \label{eq:insample_softmax}
% \end{align}
% By choosing the maximizer policy the above equation takes the form:
\begin{align}
    \datasetOptimalQ (s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{\tau \ln \!\!\!\!\!\sum_{a': \datasetPolicy(a'|s') > 0} \!\!\!\!\! \exp\AdaBracket{\tau^{-1} \datasetOptimalQ(s',a')}}.
\end{align}
As the dataset support constraint poses a challenge to implementation, \citet{Xiao2023-InSampleSoftmax} proposed to transform the summation into an expectation to avoid directly computing the constraint: 
\begin{align}
    \begin{split}
    \sum_{a': \datasetPolicy(a'|s') > 0} \!\!\!\!\!\!\exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a')} &= \!\!\!\!\!\!\sum_{a': \datasetPolicy(a'|s') > 0} \frac{\datasetPolicy(a'|s')}{\datasetPolicy(a'|s')} \exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a')} \\
    &= \expectation{a'\sim\datasetPolicy(\cdot | s')}{\exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a') - \ln\datasetPolicy(a'|s')}}.
    \end{split}
\end{align}
The expectation can be approximated by Monte-Carlo sampling actions from the dataset.
Since the term $\exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a')}$ appears also in the regularized softmax policy, in-sample softmax updates the policy towards 
\begin{align}
    \pi_{\datasetPolicy, k+1} \propto  \datasetPolicy(a|s) \exp\AdaBracket{\frac{Q_{\datasetPolicy, k}(s,a)}{\tau} - \ln\hat{\pi}_{\mathcal{D}}(a|s)},
    \label{eq:inac_policy}
\end{align}
where $\hat{\pi}_{\mathcal{D}}$ inside the exponential function is learned to imitate the behavior policy to avoid $\pi_{\mathcal{D}} = 0$ leading to an unbounded log-policy.

The benefits of the in-sample softmax can be interpreted as (1) softmax is easier to compute than hard max in the continuous action setting; 
(2) the in-sample softmax policy \eq{\ref{eq:inac_policy}} can be seen as a KL-regularized policy and hence the dataset support constraint is satisfied.
In fact, the support of $ \pi_{\datasetPolicy, k+1}$ should be exactly the same as $\datasetPolicy$ since $\exp(\frac{\cdot}{\tau}) > 0$ as long as $\tau \neq \infty$.
We now explain why \eq{\ref{eq:inac_policy}} can be regarded as a KL-regularized policy: it can be decomposed into two terms:
the first term $\datasetPolicy(a|s) \exp\AdaBracket{\frac{Q_{\datasetPolicy, k}(s,a)}{\tau} }$ acts as a KL-regularized policy with respect to the behavior policy; 
the second term $\exp\AdaBracket{-\ln\hat{\pi}_{\mathcal{D}}(a|s)}$ can be seen as induced by another regularization $-\sum_{a}{\pi(a|s)}{\ln{\hat{\pi}_{\mathcal{D}}(a|s)}}$, which is the cross entropy between the in-sample softmax policy and the (learned) behavior policy.

@@

Furthermore, Tsallis policies provide an means to formulate the common assumption that actions not present in the dataset are with low probability of being selected.

@@

    Q_{t+1, \datasetPolicy}(s,a) &= r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_{\mathcal{D}}(s)} \!\!\!\!\! \pi_{t}(a'|s') \AdaBracket{Q_{t, \datasetPolicy}(s',a') - \tau S_q(\pi_{t}(\cdot|s'))}}.

@@

The learned Tsallis policy maintains a new set of allowable actions $K_{t, q}$ depending on $q$ and iteration $t$.
The set satisfies the condition $K_{t, q} \preceq K_\mathcal{D}$:
 i.e. $|K_{t, q}| \leq |K_\mathcal{D}|$ and support constraint $\pi_t \preceq \datasetPolicy$.
% That is, the backward Bellman optimality equation becomes:
%         \datasetOptimalQ(s,a) &= r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')}}. 
% The term inside the expectation is now:
%         & \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')} \\ 
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') + \frac{\tau}{2}(1 - \pi_{*, \datasetPolicy}(a'|s')) } \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') - \frac{\tau}{2}\pi_{*, \datasetPolicy}(a'|s') } + \frac{\tau}{2} \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \frac{\AdaRectBracket{ \tau^{-1}Q_{t, \datasetPolicy}(s,a)}_+ }{\sum_{b\in K_\mathcal{D}(s')}\tau^{-1} Q_{t, \datasetPolicy}(s,b)}

@@

    \KLany{\pi_t(\cdot|s)}{\datasetPolicy(\cdot|s)} \leq K_{t}(s)\! \AdaRectBracket{  { \pi_{t}^{q}(a|s) - \pi_{t}^{q-1} (a|s) } + \pi_t(a|s) - \frac{q-3}{q-1}  + \datasetPolicy^{q-2}(a|s) - \datasetPolicy^{q-1}(a|s)}.

@@

\textbf{In-sample Tsallis Policy Estimation}
Similar to \cite{Xiao2023-InSampleSoftmax}, we want to directly use the actions from the dataset to estimate our policy.
We do a similar step to \eq{\ref{eq:inac_policy}}:
\begin{align}
    \begin{split}
        &\pi_{\datasetPolicy, k+1} (a|s) \propto \exp_q \AdaBracket{\frac{1}{\tau} Q_{t, \datasetPolicy}(s,a)} = \datasetPolicy(a|s) \datasetPolicy(a|s)^{-1} \exp_q\AdaBracket{\frac{1}{\tau}Q_{t, \datasetPolicy}(s,a)} \\
        &= \datasetPolicy(a|s)  \exp_q{\AdaBracket{\ln_q{\frac{1}{\datasetPolicy(a|s)}}}} \exp_q\AdaBracket{\frac{1}{\tau}Q_{t, \datasetPolicy}(s,a)}\\
        &=  \datasetPolicy(a|s) {\AdaBracket{ \exp_q\AdaBracket{\frac{1}{\tau}Q_{t, \datasetPolicy}(s,a) + \ln_2\frac{1}{\datasetPolicy(a|s)}}^{q-1} - (q-1)^2 \frac{1}{\tau}Q_{t, \datasetPolicy}(s,a)  \ln_q{\frac{1}{\datasetPolicy(a|s)}} }^{\frac{1}{q-1}}}.
        \label{eq:tsallis_inac_policy_thoery}
    \end{split}
\end{align}
In the last step we made use of the relationship $\AdaBracket{\expq{x}\cdot \expq{y}}^{q-1} = \expq{\AdaBracket{x+y}}^{q-1} + (q-1)^2 xy$ \cite{Yamano2004-properties-qlogexp}.

>>>>

We can write out the regularized policy for general Tsallis entropy regularization for any $q$\footnotemark\footnotetext{Different to prior works \cite{Lee2018-TsallisRAL,Nachum18a-tsallis}, our definition of $\psi$ has an additional $\frac{1}{q-1}$ term to accommodate the $q$-exponential policy, see Appendix \ref{apdx:derivation} for derivation.}:
\begin{align}
    \pi(a|s) = \exp_q \AdaBracket{\frac{Q(s,a)}{\tau } - {\psi}\AdaBracket{\frac{Q(s, \cdot)}{\tau }}}, \,\,
    {\psi}\AdaBracket{\frac{Q(s,\cdot)}{\tau}} \doteq \frac{\sum_{a\in K(s)} \frac{Q(s,a)}{\tau} - 1 }{|K{(s)}|} + \frac{1}{q-1}.
    \label{eq:tsallis_policy}
\end{align}
  $K(s)$ is the set of highest-value actions satisfying $1 \!+\! i\frac{Q(s,a_{(i)})}{\tau} \!>\! \sum_{j=1}^{i}\frac{Q(s,a_{(j)})}{\tau}$, with $a_{(j)}$ denotes the $j$-th largest action.
  Intuitively, the policy first sorts actions by $a_{(1)}, \dots, a_{(|\mathcal{A}|)}$ and then compute the threshold $\psi$.
  Suppose $Q(s, a_{(j+1)}) \leq \psi \leq Q(s, a_{(j)})$, then all actions from $j+1$ are truncated and have zero probability of being selected.
  The truncation effect can be controlled by $\tau$.

@@

It is worth noting that unlike for online RL, where the OOD actions can lead to sampling more around the low sample region and eventually correction of the values, in offline RL this is impossible.
Instead, many of the existing works propose to force the learned policy to be close to the behavior policy \cite{Dadashi2021-pseudoMetricOffline,Fujimoto2019-InSampleMax,Fujimoto2021-minimalist,Nair2021-awac}.
This is often achieved by adding a regularizer in the policy update penalizing deviating from the behavior policy \cite{Ghasemipour2021-EMaQ,Kumar2019-BootstrapErrorQlearningMMD,Jaques2020-OfflineDialog,Wu2020-BehaviorRegularizedAC}, e.g. by incorporating KL divergence $\max_{\pi}\expectation{s\sim\mathcal{D}}{\expectation{a\sim\pi(\cdot|s)}{Q(s,a)} - \tau\KLany{\pi(\cdot|s)}{\datasetPolicy(\cdot|s)}}$.
The critic is typically updated by minimizing the loss $\mathbb{E}_{(s,a,s')\sim \mathcal{D}}\expectation{a\sim\pi(\cdot|s)}{\AdaBracket{ r(s,a) + \gamma Q(s',a') - Q(s,a)}^2}$.
The regularization leads to the policy form $\pi(a|s)\propto\datasetPolicy(a|s)\exp\AdaBracket{\tau^{-1}Q_{\pi}(s,a)}$ where the learned policy must have the same support of the behavior policy.
This idea is shared by the \emph{in-sample} methods that enforce the support of the learned policy to be within the behavior policy $\pi \preceq \datasetPolicy$ \cite{Fujimoto2019-InSampleMax,Kostrikov2022-implicitQlearning,Xiao2023-InSampleSoftmax}, which is achieved by only updating for the actions in the dataset.

@@

To alleviate the OOD error, \citet{Fujimoto2019-InSampleMax} proposed the in-sample Bellman optimality equation to update only for actions present in the dataset:
\begin{align}
    \datasetOptimalQ(s,a) = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{\max_{a': \datasetPolicy(a'|s') > 0} \datasetOptimalQ(s',a')}.
    \label{eq:hardmax_offline}
\end{align}
Later, \citet{Xiao2023-InSampleSoftmax} proposed in-sample softmax to better estimate the policy inside the bracket since in the continuous case the hard max operator might be difficult to solve for.
By regularizing with the Shannon entropy $\tau \entropy$ and imposing the dataset support constraint, the in-sample softmax Bellman optimality equation has the following evaluation step:
% \begin{align}
%     \datasetOptimalQ(s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a': \datasetPolicy(a'|s') > 0} \!\!\!\!\! \pi(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau\entropy(\cdot|s')}}.
%     \label{eq:insample_softmax}
% \end{align}
% By choosing the maximizer policy the above equation takes the form:
\begin{align}
    \datasetOptimalQ (s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{\tau \ln \!\!\!\!\!\sum_{a': \datasetPolicy(a'|s') > 0} \!\!\!\!\! \exp\AdaBracket{\tau^{-1} \datasetOptimalQ(s',a')}}.
\end{align}
As the dataset support constraint poses a challenge to implementation, \citet{Xiao2023-InSampleSoftmax} proposed to transform the summation into an expectation to avoid directly computing the constraint: 
\begin{align}
    \begin{split}
    \sum_{a': \datasetPolicy(a'|s') > 0} \!\!\!\!\!\!\exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a')} &= \!\!\!\!\!\!\sum_{a': \datasetPolicy(a'|s') > 0} \frac{\datasetPolicy(a'|s')}{\datasetPolicy(a'|s')} \exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a')} \\
    &= \expectation{a'\sim\datasetPolicy(\cdot | s')}{\exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a') - \ln\datasetPolicy(a'|s')}}.
    \end{split}
\end{align}
The expectation can be approximated by Monte-Carlo sampling actions from the dataset.
Since the term $\exp\AdaBracket{\tau^{-1}\datasetOptimalQ (s',a')}$ appears also in the regularized softmax policy, in-sample softmax updates the policy towards 
\begin{align}
    \pi_{t+1,\datasetPolicy} \propto  \datasetPolicy(a|s) \exp\AdaBracket{\frac{Q_{t, \datasetPolicy}(s,a)}{\tau} - \ln\hat{\pi}_{\mathcal{D}}(a|s)},
    \label{eq:inac_policy}
\end{align}
where $\hat{\pi}_{\mathcal{D}}$ inside the exponential function is learned to imitate the behavior policy to avoid $\pi_{\mathcal{D}} = 0$ leading to an unbounded log-policy.

The benefits of the in-sample softmax can be interpreted as (1) softmax is easier to compute than hard max in the continuous action setting; 
(2) the in-sample softmax policy \eq{\ref{eq:inac_policy}} can be seen as a KL-regularized policy and hence the dataset support constraint is satisfied.
In fact, the support of $ \pi_{\datasetPolicy, k+1}$ should be exactly the same as $\datasetPolicy$ since $\exp(\frac{\cdot}{\tau}) > 0$ as long as $\tau \neq \infty$.
We now explain why \eq{\ref{eq:inac_policy}} can be regarded as a KL-regularized policy: it can be decomposed into two terms:
the first term $\datasetPolicy(a|s) \exp\AdaBracket{\frac{Q_{t, \datasetPolicy}(s,a)}{\tau} }$ acts as a KL-regularized policy with respect to the behavior policy; 
the second term $\exp\AdaBracket{-\ln\hat{\pi}_{\mathcal{D}}(a|s)}$ can be seen as induced by another regularization $-\sum_{a}{\pi(a|s)}{\ln{\hat{\pi}_{\mathcal{D}}(a|s)}}$, which is the cross entropy between the in-sample softmax policy and the (learned) behavior policy.

@@

Furthermore, Tsallis policies provide an means to formulate the common assumption that actions not present in the dataset are with low probability of being selected \cite{Kostrikov2021-fisherCriticReg}.

@@

    Q_{t+1, \datasetPolicy}(s,a) &= r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_{\mathcal{D}}(s)} \!\!\!\!\! \pi_{t+1}(a'|s') \AdaBracket{Q_{t, \datasetPolicy}(s',a') - \tau S_q(\pi_{t+1}(\cdot|s'))}}.

@@

The term inside the bracket is known as $q$-maximum \cite{Lee2020-generalTsallisRSS}.
Similar to the softmax operators \cite{asadi17a,azar2012dynamic}, $q$-maximum is an approximation to the maximum with degree controlled by $q$.

More importantly, the support constraint is naturally satisfied since 
the learned Tsallis policy learns a new set of allowable actions $K_{t, q}$ from $K_\mathcal{D}(s)$ depending on $q$ and iteration $t$.
The set satisfies the condition $K_{t, q} \preceq K_\mathcal{D}$:
 i.e. $|K_{t, q}| \leq |K_\mathcal{D}|$ and support constraint $\pi_t \preceq \datasetPolicy$.
 Let us take $q=2$ for example:
 \begin{align}
    \begin{split}
    &Q_{t+1, \datasetPolicy}(s,a) = r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_{\mathcal{D}}(s)} \!\!\!\!\! \pi_{t+1}(a'|s') \AdaBracket{Q_{t, \datasetPolicy}(s',a') - \tau S_2(\pi_{t+1}(\cdot|s'))}}\\
    &\qquad = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{ \tau\sum_{a' \in K_{\mathcal{D}}(s)} \!\! \AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}}^2 - \AdaBracket{ \psi\AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}} - 1 }^2 + \tau}\\
    &\qquad = r(s,a) + \gamma \expectation{s'\sim P(\cdot | s,a)}{ \tau\sum_{a' \in K_{t,q}(s)} \!\! \AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}}^2 - \AdaBracket{ \psi\AdaBracket{\frac{Q_{t, \datasetPolicy}(s',a')}{\tau}} - 1 }^2 + \tau}.
    \end{split}
    \label{eq:tsallis_backward_q2}
 \end{align}
 The second equation is because $\max_{\pi}\sum_{a\in\pi(\cdot|s)}\pi(a|s)Q(s,a) - \tau S_2(\pi(\cdot|s))$ attains its maximum at $\tau \sum_{a \in K(s)}\AdaBracket{ \frac{Q(s,a)}{\tau} }^2 - \psi\AdaBracket{\frac{Q(s, \cdot)}{\tau}}^2 + \tau$ \cite{Lee2018-TsallisRAL,Martins16-sparsemax}, and the last equation is due to $K_{t, q} \preceq K_\mathcal{D}$.
 \eq{\ref{eq:tsallis_backward_q2}} states that, one needs not to explicitly enforce the support constraint since it is automatically fulfilled by learning a new subset of allowable actions.
% That is, the backward Bellman optimality equation becomes:
% \begin{align}
%     \begin{split}
%         \datasetOptimalQ(s,a) &= r(s,a) +  \gamma \expectation{s'\sim P(\cdot | s,a)}{ \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')}}. 
%     \end{split}
% \end{align}
% The term inside the expectation is now:
% \begin{align}
%     \begin{split}
%         & \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{\datasetOptimalQ(s',a') - \tau S_2(\pi_{*, \datasetPolicy})(\cdot|s')} \\ 
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') + \frac{\tau}{2}(1 - \pi_{*, \datasetPolicy}(a'|s')) } \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \pi_{*, \datasetPolicy}(a'|s') \AdaBracket{ \datasetOptimalQ(s',a') - \frac{\tau}{2}\pi_{*, \datasetPolicy}(a'|s') } + \frac{\tau}{2} \\
%          &= \sum_{a' \in K_\mathcal{D}(s')} \frac{\AdaRectBracket{ \tau^{-1}Q_{t, \datasetPolicy}(s,a)}_+ }{\sum_{b\in K_\mathcal{D}(s')}\tau^{-1} Q_{t, \datasetPolicy}(s,b)}
%     \end{split}
% \end{align}

@@

    \KLany{\pi_t(\cdot|s)}{\datasetPolicy(\cdot|s)} &\leq \!\!\!\!\!\! \sum_{a\in K_{t,q}(s)}\!\!\!\!\! \pi_t(a|s)\AdaRectBracket{  { \pi_{t}^{q}(a|s) - \pi_{t}^{q-1} (a|s) } + \pi_t(a|s) - \frac{q-3}{q-1}  + \datasetPolicy^{q-2}(a|s) - \datasetPolicy^{q-1}(a|s)} \\
    &\leq K_{t,q}(s)\!\AdaRectBracket{  { \pi_{t}^{q}(a|s) - \pi_{t}^{q-1} (a|s) } + \pi_t(a|s) - \frac{q-3}{q-1}  + \datasetPolicy^{q-2}(a|s) - \datasetPolicy^{q-1}(a|s)}.

@@

\textbf{In-sample Tsallis Policy Estimation}
Similar to \cite{Xiao2023-InSampleSoftmax}, we want to directly use the actions from the dataset to estimate our policy.
We do a similar step to \eq{\ref{eq:inac_policy}}:
\begin{align}
    \begin{split}
        &\pi_{t+1,\datasetPolicy} (a|s) \propto \exp_q \AdaBracket{\frac{1}{\tau} Q_{t, \datasetPolicy}(s,a)} = \datasetPolicy(a|s) \datasetPolicy(a|s)^{-1} \exp_q\AdaBracket{\frac{1}{\tau}Q_{t, \datasetPolicy}(s,a)} \\
        &= \datasetPolicy(a|s)  \exp_q{\AdaBracket{\ln_q{\frac{1}{\datasetPolicy(a|s)}}}} \exp_q\AdaBracket{\frac{1}{\tau}Q_{t, \datasetPolicy}(s,a)}\\
        &=  \datasetPolicy(a|s) {\AdaBracket{ \exp_q\AdaBracket{\frac{1}{\tau}Q_{t, \datasetPolicy}(s,a) + \ln_q\frac{1}{\datasetPolicy(a|s)}}^{q-1} - (q-1)^2 \frac{1}{\tau}Q_{t, \datasetPolicy}(s,a)  \ln_q{\frac{1}{\datasetPolicy(a|s)}} }^{\frac{1}{q-1}}}.
        \label{eq:tsallis_inac_policy_thoery}
    \end{split}
\end{align}
In the last step we made use of the relationship $\AdaBracket{\expq{x}\cdot \expq{y}}^{q-1} = \expq{\AdaBracket{x+y}}^{q-1} + (q-1)^2 xy$ \cite{Yamano2004-properties-qlogexp}.
